\begin{comment}
- Papers included in thesis
- Content of papers (objectives/methods/Preliminary results)
\end{comment}

\section{Edna}

Users today give web applications their data but have little control over how
these applications store and protect this data.  Giving users control is
challenging for developers, as application functionality sometimes requires the
very same data that users want to protect.

Edna is a library that lets web application developers give users flexible and
correct control over their data’s exposure without breaking the application.
Edna minimizes application changes and developer effort, and enables
applications to securely hide user data and users to later restore it.  Edna
introduces abstractions for \emph{sealing}, which selectively renders user data
inaccessible via encryption, and \emph{revealing}, which enables the owning
user to restore their data to the application.

We implemented a prototype of Edna, and evaluated it with three real-world web
applications: Lobsters, a discussion forum; HotCRP, a conference review system;
and WebSubmit, a homework submission application. Integrating Edna into these
applications required minor code changes. For example, supporting three types of
sealing in the 160k-LoC Lobsters application required adding 697 LoC. The
modified applications retained their expected semantics and functionality.
Edna's sealing and revealing performance depends on the amount of data affected,
but they generally complete in seconds and have a small effect on the
performance of concurrent operations.

In this thesis, I will discuss Edna's relationship to prior research, its
limitations, and the following contributions:
\begin{enumerate}[nosep] 
    \item A new paradigm for developers to provide flexible user control over data in web applications, with cryptographic protection and while maintaining application functionality and invariants.
    \item Abstractions for sealing and revealing, and a small set of data-anonymizing primitives (remove, modify, decorrelate) that cover a wide range of application needs and compose cleanly.
    \item The design and implementation of Edna, our prototype library that implements user data control via sealing and revealing, as well as Ednacrypt, which additionally encrypts unsealed data.
    \item Case studies of integrating Edna with three real-world web applications, an evaluation of Edna's effectiveness, performance, and security, and a comparison to Qapla.
\end{enumerate}

\begin{comment}

Edna is complementary to existing data protection mechanisms. For example, we
combine Edna with an encrypted database to achieve stronger guarantees.
Ednacrypt simultaneously protects against database server compromises even for
unsealed data and adds Edna's protections for sealed data to encrypted
databases, which have no built-in support for removing sensitive data without
breaking the application.

To investigate the need for Edna as a new system, we tried to realize Edna's
functionality atop Qapla~\cite{qapla}, a framework that rewrites SQL queries to
conform to access control policies. We found that Qapla requires invasive
application changes, its abstractions are awkward for sealing and revealing, and
Qapla's query rewriting slows down common queries.

%Edna has some limitations. Its usability goals, and specifically the fact that
%placeholder data continues to exist in the database, prevent Edna from
%protecting against inference attacks (\eg statistical correlation attacks). Edna
%also assumes bug-free seal specifications, and that applications use
%Edna correctly. Finally, Edna provides limited protection for sealed data
%against attackers who compromise the database server, as auxiliary database
%information (\eg logs) may contain old plaintext data; Ednacrypt strengthens
%these protections.

\end{comment}


\section{Hydra}

Hydra narrows down on a specific aspect of Edna, namely how users control their
identities and links between their identities and data in web applications.
Users today will 

Users often want to 
Hydra specifically on 

In Hydra, users authenticate with an application like normal,

Finstas (fake instagrams), Reddit throwaways. 
Multi-account containers in Firefox let users act as distinct identities as they
browse the web.


\section{Funhouse}
