Users have tens to hundreds of accounts with web services that store
sensitive data, from social media to tax preparation and e-commerce
sites~\cite{tens,hundreds,password_life_cycle}.
%
While users have the right to delete their data (via \eg the
GDPR~\cite{eu:gdpr} or CCPA~\cite{ccpa}), more nuanced
data controls often don't exist.
%
For example, a user might wish to hide and protect their profiles on an
e-commerce or dating app when inactive, and to recover their accounts should
they return to use the application. 
%
However, services often provide only coarse-grained, blunt tools that
result in all-or-nothing exposure of users’ private data.
%

%
This thesis introduces the notion of \emph{disguised data}, a reversible state
in which sensitive data is hidden.
%
To demonstrate the feasibility of disguised data, this thesis also presents
\sys---the first system for disguised data---which helps database-backed web
applications provide new privacy features for users, such as 
removing their data without permanently losing their accounts, anonymizing their
old data, and selectively dissociating personal data from public profiles.
%
\sys helps developers support these features while maintaining application
functionality and referential integrity in the database via \emph{disguising} and
\emph{revealing} transformations.
%
Disguising selectively renders user data inaccessible via encryption, and
revealing restores their data to the application.
%
\sys's techniques allow transformations to compose in any order, \eg deleting a
previously anonymized user's account, or restoring an account back to an
anonymized state.
%

%
With \sys, web applications can enable flexible privacy features with reasonable
developer effort and moderate performance impact on application operation
throughput.
%
In the Lobsters social media application---a 160k LoC web application with >16k
users---adding \sys and its features takes <1k LoC, and decreases throughput
1--7\% in the common case and up to 28\% when a heavy user
who owns 1\% of all application data continuously disguises and reveals their
account.
%

%This thesis and \sys thus demonstrate that with disguised data, applications
%can support flexible privacy features beyond what they offer users today.
%\lyt{I want to end with something a bit more summary, but not sure this is the
%right way?}
%developed and available to users.
%
