%
This thesis builds upon prior work on \sys published at SOSP 2023~\cite{edna}.
I am immensely grateful to my collaborators on \sys over the many years: Hannah
Gross, Eddie Kohler, Malte Schwarzkopf, and Frans Kaashoek. Without you all,
\sys would not exist today.
%
I would like to thank Akshay Narayan, Anish Athalye, Aurojit Panda, Derek
Leung, Gohar Irfan Chaudhry, Henry Corrigan-Gibbs, James Mickens, Kevin Liao,
Kinan Dak Albab, Matthew Lentz, Nick Young, Nickolai Zeldovich, MIT's PDOS
group, Brown's ETOS group, the SystemsResearch@Google Team, and all our
anonymous reviewers: you generously donated your time and insights that greatly
improved \sys. 
%

%
While working on \sys, I am grateful to have been supported by an NSF Graduate
Research Fellowship, NSF awards CNS-2045170 and CSR-1704376, a Google Research
Scholar award, and funding from VMware.
%
CloudLab~\cite{cloudlab} also provided essential resources
to develop the \sys prototype and evaluate its artifact.
%

%
\sys and this thesis would not have been possible without the many people whose
advice, support, generosity, and kindness have carried me throughout the past
six-plus years.
%
I thank you all not just for \sys, but also for encouraging me to be better in
all ways: as a thinker, a collaborator, a friend, and a human being.
%
I would especially like to thank:

\begin{center}{My Family}\end{center}
    \begin{itemize}
    \item Phaih-lan Law and Kenwood Tsai, who raised me and still love me despite my many flaws. 
    
    \item Stephanie ("Stephie"), my forever role model. 
     
     \item Ah-ma and Ah-gong, who continue to show me how to embrace life to its fullest. 
        
    \item Aunty Cecilia, Uncle Jacek, Ah-Ee, Aunty Sally, Tua-ku, Jackie,
        Wei-Jen, Trevor Hohn, and many aunts, uncles, and cousins, for welcoming
            me home across the country and around the world.

    \item Benji, for the light you have brought into my life.
    \end{itemize}

\begin{center}{My Mentors and Role Models}\end{center} 
    \begin{itemize} 
        \item Eddie Kohler, Malte Schwarzkopf, Frans Kaashoek, James
                Mickens, Peter Druschel, Derek Dreyer, Stefan Saroiu, Margo
                Seltzer, Kim Keeton, Anastasia Ailamaki, Phillip Levis, Joel
                Emer, Mathilda van Es, Julia Netter, Alexander Kojevnikov, and
                Ellen Feigenbaum; for catching me when I stumble, and showing me
                the many different ways to live life well.

        \item My Advisors---Malte Schwarzkopf, Frans Kaashoek, and Eddie
            Kohler---for their unwavering belief in me and my research; I will
            constantly be in admiration of your endless energy and persistent
            curiousity.

        \item My PDOS and MIT peers---Alexandra Henzinger, Anish Athalye,
            Ariel Szekely, Baltasar Dinis, Ben Holmes, Derek Leung, Gohar Irfan
            Chaudhry, Hannah Gross, Josh Fried, Ryan Lehmkuhl, Sanjit Bhat,
            Upamanyu Sharma, Yun-Sheng Chang, Zain Ruan, Inho Cho, Akshay
            Narayan, Tej Chajed, Ataley Mert Ileri, Jon Gjengset, Frank
            Cangialosi, Vibhaalakshmi Sivaraman, Joseph Tassarotti, Ralf Jung,
            Adam Belay, Henry Corrigan-Gibbs, Nickolai Zeldovich, and Robert
            Morris---for providing an inspiring community and home away from home.
       % \item The many people who helped me heal through the obstacles that
       %     landed in my path during the past decade.  
    \end{itemize}
    
\begin{center}{My (Other) Families}\end{center} 
    \begin{itemize}
    \item My Musical Family: Solon Gordon, Jenn Chang, Valerie Chen, Lynn Chang,
        Lisa Wong, Ken Allen, Mary Jane, and the many more who have shared their
            music with me; and Music for Food and Sharing Notes at MIT for
            enabling me to give back---even just a little---to the MIT and
            broader Boston communities with music.    

    \item My Climbing/Running Family: Anders Simpson-Wolf, Lekha Jananthan, Whitney
        Meza, Oliver Thomas, Rick Wainner, Bess and Chris, John Langan, and the
            others who helped me become the strongest I've ever been.

    \item My Friends, all of whom I am very lucky to have met: Serena Booth (and
        Ducki Booth), Valerie Chen, Melissa Wen, Roberta De Viti, Lara Booth,
            Daniel Rothchild, Ethan Tsai, Hanson Tam, Kevin Liao, Matthew Lentz,
            Nikhil Benesch, Samyu Yagati, Anitha Gollamudi, Solon Gordon, Jenn
            Chang, Anders Simpson-Wolf, Lekha Jananthan, Serena Wang, Zachary Munro,
            James Deng, Wentong Zhang, Ashvin Swaminathan, Karima Ma, James
            Tompkin, Helena Caminal, Hamish Nicholson, Henry Burnam, Kevin
            Loughlin, and Yihe Huang---I look forward to the many adventures
            awaiting us.
    \end{itemize}
 
