%
\sys's prototype consists of \lyt{TODO}k lines of Rust.
%(1.6k LoC specifically added for \syscrypt).
%
\sys also provides an API server that exposes a JSON-HTTP API that applications
can use to invoke \sys.
%
%In the following, we discuss key implementation details that \sys relies for
%security and performance.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{API.}
\label{s:api}
%
An application can use the prototype if:
\one{} it uses a MySQL database;
\two{} rows to \xx have direct foreign key relationships to a users table,
where each user corresponds to a row of that table;
\three{} all rows to \xx are owned by one or more principals; and
\four{} all rows can be uniquely identified (\eg via primary key).
%
Applications that do not satisfy these assumptions---\eg because they have
complex ownership chains or use a NoSQL database---could be supported with
extensions to the prototype.

\iffalse
\begin{figure}[t]
\begin{lstlisting}[style=rust,escapeinside={(*}{*)}]
// Generates keypair for p and returns
// the user's backup credential
(*\textbf{RegisterPrincipal}*)(p: UID, pw: Password,
        pubkey: PublicKey, privkey: PrivKey)
    -> Credential;
// \xxs principal p according to the spec,
// optionally over already-\xxed data ((*\S\ref{s:composition}*))
(*\textbf{\xxData}*)(p: Option<UID>, spec: \xxSpec,
    \xx_over: Option<(
        Credential,
        Vec<Locator>
    )>) -> (\xxID, Vec<Locator>);
// Reveals data \xxed by s for p with p's
// private key.
// locs point to bags p can decrypt
(*\textbf{RevealData}*)(p: Option<UID>, s: \xxID,
    cred: Credential, locs: Vec<Locator>);
// Gets principals at loc that p can speak-for.
(*\textbf{CanSpeakFor}*)(p: UID, cred: Credential,
    loc: Locator) -> Vec<UID>;
\end{lstlisting}
\caption{\sys's high-level API (Rust-like syntax).}
\label{f:api-high}
\end{figure}
%
\fi


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Secure Record Storage.}
%\sys stores the \xx and principal tables in the database.
%
When encrypting diff and speaks-for records, \sys appends a random nonce to
the record plaintext to prevent known-plaintext attacks.
%
It then generates a new public/private keypair for x25519 elliptic curve key
exchange.
%
Using the newly created private key and the principal's public key, \sys
performs the x25519 elliptic curve Diffie-Hellman ephemeral key exchange to
generate a shared secret.
%
\sys encrypts the record data with the shared secret, and saves the
ciphertext along with the freshly generated public key (required to decrypt
the data given the principal's private key).
%
This public key algorithm lacks key anonymity, so an attacker can determine
which records belong to the same principal, but this is not
fundamental~\cite{anonymous-keys}.

%Locators group together related diff and speaks-for records by principal and
%transformation; they are opaque in order to hide the principal's identity.
%
%Maintaining a locator set allows \sys's to easily find which records correspond
%to a principal's \xxed data to \eg reveal it (\S\ref{s:reveal}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%i
\section{Reveal Credentials.}
%
Our prototype supports two forms of reveal credentials: \one{} private keys; or
\two{} principals' passwords, and recovery
tokens in case they forget their passwords.
%
If an application chooses to use the latter, it provides the principal's password
to \sys upon user registration.
%
Our prototype uses a variant of Shamir's Secret Sharing~\cite{secretsharing}
to generate three shares from the private key, any two of which can reconstruct the
private key.
%
Shares are $(x, f(x) \bmod p)$ tuples, where $f(x) = \fn{privkey} + \fn{rand} \cdot
x$ and $p > \fn{privkey}$ is a known prime.
%
One share derives $x$ from the user's password using a Password-Based Key
Derivation Function (PBKDF)~\cite{pbkdf-rfc}.
%
\sys stores the resulting $f(x)$ half of the share, allowing \sys to derive one
full share from the password.
%
%\sys generates the remaining two shares via randomly sampled $x$ coordinates.
%
\sys returns the second full share as a recovery token and stores the third full
share.
%
\sys can combine this third share with the recovery token
or a full share derived from the password to recover the
private key.
%if the user provides either
%their recovery token, or their password (from which \sys derives a full share).
%either derived from the password, or the recovery token.}
%
%if \sys obtains one additional share from either the password or from a recovery token,
%\sys can recover the private key.}

The PBKDF ensures that \sys cannot guess the password-derived value with
dictionary and rainbow table attacks~\cite{pbkdf}, and that \sys cannot brute force
the recovery token.
%
%\sys cannot reconstruct the private key without either the backup share or the
%other half of the password-derived share, and \sys cannot brute force the
%value of the backup share.
%

%
%\sys stores its shares---both its full share, and its half of the
%password-derived share---at an index equal to the hash of the user's ID and
%password in a separate shares table.
%%
%If the user loses their password and instead provides their recovery
%token, the user also provides this index so \sys can efficiently find the
%relevant shares.
%\sys thus returns both the backup share and the index as backup credentials in
%\fn{RegisterPrincipal}.
%
%\sys derives the private key given either form of credentials: given the user's
%password, \sys reconstructs the third share as well as the index; or, if the
%user forgets their password, they can provide the backup credentials instead.
%\sys combines the derived share with the one it stored to reconstruct the
%private key.

%When principals change their passwords or keypairs, applications re-register the
%principal with \sys.
%%
%To change a password, the principal provides their existing
%credentials (password or backup) and new password; \sys then derives
%their private key, redoes the secret sharing process described with the
%new password, and returns the new backup credential.
%%
%Users can similarly change their public/private keypair.
%%

%
Password-based secret-sharing is only one possible implementation for backup
secrets; \sys could also support password-based backup secrets by \eg storing an
version of the private key encrypted with the user's password.
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%i
\section{Application Updates Replay Log}
\sys represents updates as pure Rust functions from database objects (represented as
$<$table, row$>$ pairs) to a new set of database objects. \sys stores the log as
a vector of updates with timestamps; this log is currently not persisted, and
updates will have to be reregistered with \sys if the application server fails.
\todo{should we persist?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%i
\section{Diff Records}
Diff records store a pair of $<$oldRows, newRows$>$ database objects.  Each
object is represented as a $<$table, row$>$ pair.  Each diff record also encodes
the type of disguise operation (remove, modify, decorrelate), the current
timestamp, and the relevant
disguise ID.

\begin{itemize}[nosep]
    \item Remove diff records contain only the removed row and no 
        new row;
    \item Modify diff records contain the row with the original value, and the
        row with the updated value; and
    \item Decorrelate diff records contain the referencing row with the original
        foreign key value, the referencing row with the new foreign key value,
        and the new pseudoprincipal row.
\end{itemize}

\sys also stores a special type of remove diff record that contains the
principal's ID and the principal's public key when removing a principal object.
This allows \sys to restore the principal to \sys's principal table when revealing
a disguise that removed the principal.

%
For efficiency, \sys batches the deletion of rows from the same table, and the
creation of pseudoprincipals upon disguise. 
%
\sys also batches the deletion of pseudoprincipals during reveal. However, \sys
does not batch insertion of other table rows during reveal, as each row's
foreign key dependencies and relevant application updates need to be applied to
each row; however, with careful implementation, \sys could support batching of
all insertions.  \todo{TODO should we batch other tables? it's much more
complex}.
%
\sys performs decorrelation and modification operations individually for each
row during both disguise and reveal, as different rows are updated to different
values.
%

%
When revealing a diff record, \sys applies all updates in the replay log with
timestamps greater than that of the diff record to the diff record's oldRows and
newRows. 
%
\sys then performs consistency checks to ensure that it can reveal the updated
diff record rows.
%
For efficiency, \sys will check to see if any new row matches the identifiers
(\eg a primary key) of an old row, and update the relevant columns of the new
row instead of removing the new row and restoring the old row.
%
Otherwise, \sys will remove the updated newRows and restore the updated oldRows.
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%i
\section{Speaks-for Chains}

Speaks-for records contains a pair of (original principal, pseudoprincipal) IDs
encoded as MySQL values, and the pseudoprincipal’s private key encoded as bytes. 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%i
\section{Joint Ownership for Shared Data}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%i
%
\section{Concurrency.}
%
\sys runs \xxing and revealing transformations in transactions, providing
serializable isolation to application users.
%
If a query within a transformation fails, the entire transformation aborts
(returning an error to the application).
%
\sys provides an option to run long-running transformations that
touch large amounts of data (\eg anonymization of all users' posts) without a
transaction, at the expense of clients potentially observing intermediate
states.
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%i
%\head{Pre-generated Pseudoprincipal Keypairs.}
%%
%Generating a single private-public keypair is expensive ($\approx$300ms), but
%decorrelating disguises require creating many pseudoprincipals.
%%
%To make pseudoprincipal creation cheap, \sys maintains a pool of
%pregenerated keypairs for pseudoprincipals that it periodically refreshes.
%%
%The application tells \sys an appropriate size for the pool (\eg an upper bound
%on how much data a user might have).
%%
%If an attacker compromises the key pool, an admin must generate a new key pool and
%reset any public/private keypairs that were accessed since the compromise.
%%but \sys makes no security guarantees
%%about  the point when the compromise happens.
%
%%To recover, an admin must generate a new key pool and reset
%%extant principals' keys.
%

%Security against an attacker who compromises the server and observes future
%disguises is unaffected, as \sys only keys from the pool when it generates
%pseudoprincipals during disguises (when the keys would otherwise have been
%generated, and leaked to the attacker).
%%
%However, an attacker who compromises the server, exfiltrates the keys, and
%leaves would be able to come back and use the keys later to reveal disguised
%data.
%%
%A fixed-size pool and periodic refreshes bound the period of vulnerability and
%amount of data such an attacker can reveal.
%

